---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# The RAMS App

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The RAMS App is a Shiny application designed for faciliating the Risk Assessment Methods for Salmon (RAMS) process.

The App can be run locally on a machine with the R software installed. A live online version is available at [RAMSalmon.com](https://ramsalmon.com).

The RAMS App is still in development.

## Local Version

To run the RAMS app locally, you need to first install the RAMS package from GitHub:

```{r, eval=FALSE}
# install.packages('remotes')
remotes::install_github('blue-matter/RAMS')
```

Then load the library and run RAMS:

```{r, eval=FALSE}
library(RAMS)
RAMS()
```
